Spatial Reasoning and Data Displays

### 2015-06-22 Paper/InfoVis2015Revision/TestingVisualAptitude.Rnw
attempt at discussing related work

Here, we want to investigate the extent to which observers make use of spatial ability in their evaluation of and reasoning about statistical graphics. As a quantitative measure of how successful an evaluation is, we are making use of the lineup protocol ~~\cite{buja2009statistical, wickham2010graphical, majumder2013validation}. 
\comment{Not sure where to add the Related Work section; the introduction is really the most similar thing, but adding another sub-section in would really kill the flow of the paragraph, in my opinion.}
``Lineups" were introduced as a tool to evaluate the statistical significance of a graphical finding~\cite{wickham2010graphical}. Lineups are also useful in assessing the effectiveness of different graphical displays~\cite{hofmann2012graphical, loy:2015}. Like their police counterpart, lineups consist of several distractor plots (of randomly generated data) and one target (the data plot). 
% 
% \begin{figure}[htp]
% 
% \end{figure}

>>>>

Here, we want to investigate the extent to which observers make use of spatial ability in their evaluation of and reasoning about statistical graphics. As a quantitative measure of how successful an evaluation is, we are making use of the lineup protocol ~~\cite{buja2009statistical, wickham2010graphical, majumder2013validation}. 
\comment{Not sure where to add the Related Work section; the introduction is really the most similar thing, but adding another sub-section in would really kill the flow of the paragraph, in my opinion.}
\hhnote{I agree, it'll disrupt the flow, but we'll have to add a related work section nevertheless. We could add a bit of discussion on separating lineups from plots judging significance.}

\hhnote{ these are the references we are supposed to discuss (not sure, how to add the talbot one - that is a study extending cleveland and then heer's). first attempt: It has been shown~\citep{pak2014} that visualizations do not necessarily reflect statistical properties well or are even misleading viewers~\citep{correll2013}. Lineup tests are different as they do not ask participants to judge significances directly but are only based on comparisons. Statistical properties are then derived from this assessment.  This has been shown to be similarly powerful to standard statistical tests in situations where these classical tests hold, and more powerful in situations where conditions of classical tests are not met~\citet{majumder2013validation}. The difference between statistical properties and visualizations is very easy to explain, as statistical significance of, e.g. a correlation coefficient is based on only a few summary statistics, whereas e.g. a corresponding  scatterplot is showing a lot more details of the data which might lead participants to a different evaluation. This, however, is not a drawback of the visualization but only shows that summary statistics might not be enough to come to an appropriate conclusion \citet{anscombe:1973}. }
``Lineups" were introduced as a tool to evaluate the statistical significance of a graphical finding~\cite{wickham2010graphical}. Lineups are also useful in assessing the effectiveness of different graphical displays~\cite{hofmann2012graphical, loy:2015}. Like their police counterpart, lineups consist of several distractor plots (of randomly generated data) and one target (the data plot). 
% 
% \begin{figure}[htp]
% 
% \end{figure}
